\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-03 NAR_DRAFT.tex
add more citations

We report only precision-recall comparisons for real tumor data because in both cases the "gold" standard data sets consist of variants that were "called" by one or more variant detection pipelines, and confirmed to be present or absent.
These mutations are in some sense \textit{easy} to call, since at least one variant caller did in fact call them.
At the same time, there is no way to compute true and false negative fractions for these data sets.
As such, it is not surprising that the performance of MuTect and \batcave are similar because the universe of variants under consideration in these experiments are by definition "callable" by at least one variant detection pipeline, and MuTect is among the most sensitive and specific variant callers \cite{Griffith2015,Cibulskis2013}.
Deep sequencing experiments where a large random sample of uncalled potential variants, as well as a random sample of variant with no reads at all present, would give much-needed insight into the differences in statistical models in variant calling.

>>>>

We report only precision-recall comparisons for real tumor data because in both cases the "gold" standard data sets consist of variants that were "called" by one or more variant detection pipelines, and confirmed to be present or absent \cite{Griffith2015,Shi2018}.
These mutations are in some sense \textit{easy} to call, since at least one variant caller did in fact call them.
At the same time, there is no way to compute true and false negative fractions for these data sets.
As such, it is not surprising that the performance of MuTect and \batcave are similar because the universe of variants under consideration in these experiments are by definition "callable" by at least one variant detection pipeline, and MuTect is among the most sensitive and specific variant callers \cite{Griffith2015,Cibulskis2013}.
Deep sequencing experiments where a large random sample of uncalled potential variants, as well as a random sample of variant with no reads at all present, would give much-needed insight into the differences in statistical models in variant calling.
